Wind_analyses

### 2019-03-06 Wind_analyses.Rmd
Wind

Data/wind_data.txt(SAWS)/wind1/wind1.txt

```{r define_fun8, include=TRUE}
load_wind <- function(wind_files) {
 site_info <- sapply(strsplit(as.character(wind_files), "/"), "[[", 4)
 site_info <- sapply(strsplit(site_info, ".txt"), "[[", 1)

  wave <- read_table(wind_files, col_types = c("dddddd"),
                     col_names = c("station_number", "station_name", "date", "hour", "speed", "dir")) %>% 
       na.omit()
  return(wave)
}

tester <- map_dfr(dir("Data/wind_data.txt(SAWS)/wind1", 
                            full.names = TRUE, pattern = "*.txt"), load_wind)
```

>>>>

```{r define_fun8, include=TRUE}
# load_wind <- function(wind_files) {
#  site_info <- sapply(strsplit(as.character(wind_files), "/"), "[[", 4)
#  site_info <- sapply(strsplit(site_info, ".txt"), "[[", 1)
#   
#   wave <- read_table(wind_files, col_types = c("dddddd"),
#                      col_names = c("station_number", "station_name", "date", "hour", "speed", "dir")) %>% 
#        na.omit()
#   return(wave)
# }
# 
# tester <- map_dfr(dir("Data/wind_data.txt(SAWS)/wind1", 
#                             full.names = TRUE, pattern = "*.txt"), load_wind)

wind_1 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings="") 
colnames(wind_1) <- c("station_number", "station_name", "date", "hour", "sub", "speed", "dir")

wind_2 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings="")
colnames(wind_2) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

wind_3 <- read.delim("/home/amieroh/Documents/Masters_2019/MastersProject/Data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings="")
colnames(wind_3) <- c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir")

# Slecting the important columns for each of the datasets
wind_fix <- function(df){
wind <- df%>% 
  select(station_name, date, hour, dir, speed)
}

wind_1 <- wind_fix(df = wind_1)
wind_2 <- wind_fix(df = wind_2)
wind_3 <- wind_fix(df = wind_3)

## Renaming the sites within the wind datasets to match the name of the sites at which seawater temperature was collected
## The wind data was obtained from the SAWS and the wind stations used were the closes stations to which temperature was collected

renaming_sites_1 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("CAPE COLUMBINE"), "St Helena Bay",        
                           ifelse(station_name %in% c("KOINGNAAS"), "Hondeklipbaai",
                                ifelse(station_name %in% c("PORT NOLLOTH"), "Port Nolloth",
                                       ifelse(station_name %in% c("LAMBERTSBAAI NORTIER"), "Lamberts Bay",
                                              ifelse(station_name %in% c("LANGEBAANWEG AWS"), "Saldanha Bay
","Error"))))))
  return(sites)
}

wind_sitesmatched_1 <-  renaming_sites_1(df = wind_1)
wind_sitesmatched_1 <- wind_sitesmatched_1[-c(121352, 121353, 379892, 379893, 609324, 609325, 843506, 843507, 1014585), ]

renaming_sites_2 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("ROBBENEILAND"), "Koeberg Basin",        
                           ifelse(station_name %in% c("GEELBEK"), "Yzerfontein",
                                ifelse(station_name %in% c("DASSEN ISLAND"), "Dassen Island",
                                       ifelse(station_name %in% c("ATLANTIS"), "Koeberg Basin","Error")))))
  return(sites)
}

wind_sitesmatched_2 <-  renaming_sites_2(df = wind_2)
wind_sitesmatched_2 <- wind_sitesmatched_2[-c(228372, 228373, 313441, 313442, 364881, 364882, 557392), ]

renaming_sites_3 <- function(df) {
  sites <- df %>%
    mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Kommetjie",  
                           ifelse(station_name %in% c("CAPE TOWN - ROYAL YACHT CLUB"), "Sea Point",
                           ifelse(station_name %in% c("CAPE TOWN TABLE BAY"), "Sea Point","Error"))))
  return(sites)
}

wind_sitesmatched_3 <-  renaming_sites_3(df = wind_3)
wind_sitesmatched_3 <- wind_sitesmatched_3[-c(119317, 119318, 196551, 196552, 346759), ]

## CAPE TOWN SLANGKOP may be used for Kommetjie and for Houtbay
wind_3_HoutBay <- wind_3 %>% 
  filter(station_name == "CAPE TOWN SLANGKOP") %>% 
  mutate(temp_sites = ifelse(station_name %in% c("CAPE TOWN SLANGKOP"), "Hout Bay","Error"))

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  dplyr::rename(site = temp_sites) %>% 
  select(site, date, hour, dir, speed)
```

Things to do*******

- Match temp and wind data
- Create plots shwoing predominant wind direction during an upwelling evnt
